\section{Problem Statement} \label{sec:problem-statement}
Visitors of beer review websites often receive recommendations for beers to try out.
However, with an abundance of available recommendations to sample from the following question arises:
\begin{quote}
    \emph{``Why should I drink this beer? What is it about?''}
\end{quote}
Given a specific recommendation, users are left behind with official product descriptions and a multitude of reviews to read through.
Marketing descriptions rarely uncover the actual characteristics of a product as their goal is to instigate attention and demand.
Assuming that reviewers talk about these characteristics revealing them is possible by mining the free-form text.
Word embedding algorithms create vectorial models for a vocabulary by taking the co-occurrence statistics of a word into account.
\begin{quote}
	\emph{``You shall know a word by the company it keeps.''} \cite{Firth1957}
\end{quote}
Building vectorial representations for the reviews of a product would allow performing numerical operations on them.
The proposed \textit{Beerlytics} system aims to exploit these representations for the creation of visual product stories.
It targets consumers and visitors of beer review websites.
Ideally, the system is capable of conveying the most representative and diverse review while also highlighting the essential characteristics of the product.
The visual product stories should be both factual and stylistically pleasing.
Creating such a system would satisfy the short attention span of the current generation by supporting cognition of relevant information \cite{MicrosoftCanada2015}.
Using different word embedding algorithms in an explorative and experimental nature for modeling products through their reviews is the primary concern of this work.
Evaluating the system through user testing provides valuable insights into the preferences of users regarding visual product stories.

\begin{quote}
    \textbf{Research question:}\\
    \emph{To what extent can a product be summarized by a visual story based on associated metadata and user-contributed reviews? (RQ)}
\end{quote}

\begin{quote}
    \textbf{Further research questions:}\\
    \emph{How can user-contributed reviews support the generation of visual stories for a product? (SRQ1)}\\
    \emph{In which way is the quality of a visual story affected by using different word embedding techniques? (SRQ2)}
\end{quote}