\section{Gameplay} \label{sec:gameplay}

As previously mentioned gameplay is heavily inspired by deathrun maps, specifically the ones found in the first-person shooter \\ \mbox{Counter-Strike: Source (CSS)}.
In the case of CSS deathrun maps, the classic shooter game mode is subverted by physically separating the terrorist team from the counter-terrorist team and stripping players from their weapons.
The running players, in the counter-terrorist team, have to avoid being taken out by traps along their path in order to reach the end.
One player in the terrorist team takes the role of the trap master trying to prevent the competing team from surviving and reaching the end of the course.
Whoever reaches the end first becomes the new trap master and is considered the winner of this round.
Otherwise, if all runners are killed in the process, the trap master wins and everyone is reset back to their starting position.

Disposable Sleeves adopts this game mode and allows up to 10 concurrent players on a server.
The first player connecting to a session, usually the server host, is automatically elected as the trap master and spawns in a separate area of the level.
From this area, one-way glass allows spectating the running players without revealing the trap master's current position and attention.
On the other side, the runners spawn in a gated area in order to prevent early starts.
Once the gate starts to open, after an audible 3-second countdown, runners aim to reach the end of the course as the first player.
The course itself alternates between safe-platforms and traps which can be activated by the trap master at free will.
Consequently, running players can die by either getting caught in an active trap or by falling off the safe-platforms.
If all players become casualties before achieving their objective they are put back into the spawn-area and the gate countdown is restarted.
Similarly, should a player manage to reach the end everyone, including the trap master, is reset back to the beginning and the winner becomes the new trap master.
This cycle repeats itself in an endless playing mode until players decide to stop playing.