\section{Technical Implementation} \label{sec:implementation}

Disposable Sleeves is created using the Unity\footnote{\url{https://unity3d.com}, accessed 29-03-2018} development platform.
It is a 3D real-time multiplayer game aimed at the desktop operating systems Windows and macOS.
Primitive shapes provide the basic structure of the environment.
A range of free assets from Unity's store are used for: styling the level in a dark dungeon theme, the two player models, lighting models, and traps.
The assets can be retrieved from the store using the following keywords: MK Glass, Adam Character Pack, Dungeon Ground, Modular Medieval Lanterns, Outline Effect, Dungeon Traps, Skull Platform, and Standard Assets.

Global illumination is disabled in order to fully rely on the light sources placed within the level.
This creates a dark feeling which matches the dystopian style of Altered Carbon.
Animations for the spawn gate, trap levers and traps themselves are designed using the Unity animation editor.
Additionally, the existing assets are heavily customized to serve their specific purpose in the envisioned gameplay.

Finally, the largest chunk of time was consumed by the implementation of the networking code.
Unity provides the UNet high-level scripting API (HLAPI)\footnote{\url{https://docs.unity3d.com/Manual/UNetReference.html}, accessed 29-03-2018} to cover the basic requirements in multiplayer games.
However, implementing smooth player movement and synchronizing game state is a demanding task in any case.
In its current form, the game is fully functional to be played by multiple concurrent players.
Preferably game sessions should be held in a local area network (LAN) to minimize delays.