\section{Schedule}
Table \ref{tbl:schedule} lists weekly activities from April to July 2018.
While the schedule extends into the month of July the main thesis work will take place between 02.04. and 29.06.
Accordingly, the thesis document should be finalized before the end of June.
The absence of an activity does not signify its exclusion from other weeks, for instance preparation for writing can begin early on in the process.
In this regard, the proposed schedule can be interpreted as a roadmap with milestones which should be realized in their designated week.
Sparsity and buffer times in June and July retain flexibility of the planning and allow activities to be stretched out if necessary.

Activities in an italic font do not directly translate to actual work items, namely \textit{travel} and \textit{buffer time}.
They are included to keep an overview of where time bottlenecks could potentially arise or be resolved.
Travel activities marked with an asterisk can be rescheduled if the circumstances require more time or presence in Amsterdam.

Finally, weekly meetings have been scheduled with the supervisor which are not explicitly denoted in the schedule.
At the time of writing they will take place on Thursdays at 10 am.
They involve all other students working on the same overarching review analytics system.

\begin{table}[h]
    \centering
    \begin{tabular}{p{0.25\linewidth}p{0.67\linewidth}}
        \hline
        \emph{Week} & \emph{Activities} \\
        \hline
        \#14, 02.04.-08.04. & \textit{Travel}, building scraping system, DAS-4 introduction \\
        \#15, 09.04.-15.04. & Finish scraping system, literature study, data collection \& exploration \\
        \#16, 16.04.-22.04. & Evaluate appropriate NLP and ML techniques, related work \\
        \#17, 23.04.-29.04. & Build first summarization system \\
        \#18, 30.04.-06.05. & Writing, iterate on summarization system \\
        \#19, 07.05.-13.05. & Writing, iterate on summarization system, create first frontend, \textbf{mid-term presentation} \\
        \#20, 14.05.-20.05. & Writing, iterate on summarization system \& frontend, begin employing scoring algorithms , \textit{travel*} \\
        \#21, 21.05.-27.05. & Writing, further work on the full system, evaluation of system performance \textit{travel} \\
        \#22, 28.05.-03.06. & Writing, finalize work on summarization system \\
        \#23, 04.06.-10.06. & Writing \\
        \#24, 11.06.-17.06. & Writing, \textit{buffer time} \\
        \#25, 18.06.-24.06. & Writing, \textit{buffer time}, \textit{travel} \\
        \#26, 25.06.-01.07. & \textbf{Final submission} \\
        \hline
        \#27, 02.07.-08.07. & Prepare thesis defense, \textit{travel*} \\
        \#28, 09.07.-15.07. & Prepare thesis defense \\
        \#29, 16.07.-22.07. & \textbf{Thesis defense (Friday, 20.07.)} \\
        \#30, 23.07.-29.07. & \textit{Buffer time} \\
        \hline
    \end{tabular}
    \caption{Proposed weekly activity schedule} \label{tbl:schedule}
\end{table}